Efficient Handling of String-Number Conversion

### 2020-04-02 final-version/main.tex
Update main.tex

For ease of presentation, we  use the following toy example \changed{$$\Phi\!=\! \{``0"x\!=\! x``0", \sti{x} \!=\! \sti{y} ,|y|\!>\!|x|, 1000\!<\!|y| \}$$}
to explain the main ideas behind our decision procedure.  To make our terminology explicit: $\Phi$ states that \changed{$``0"$ concatenated with $x$ is the same as $x$ with $``0"$, the numeric value of the string $x$ is equivalent to that of $y$, $y$ is longer than $x$, and $y$ is longer than $1000$ characters.  Notice that $\Phi$ is satisfiable. E.g., it has a model $x=``00"$ and $y=``0^{1002}"$}.
\changed{Although this toy example is seemingly trivial, all the string constraint solvers we tried (including Z3, CVC4, and Z3Str3) cannot solve it within 10 minutes. }

>>>>

For ease of presentation, we  use the following toy example \changed{$$\Phi\!=\! \{``0"x\!=\! x``0", \sti{x} \!=\! \sti{y} ,|y|\!>\!|x| >1, 1000\!<\!|y| \}$$}
to explain the main ideas behind our decision procedure.  To make our terminology explicit: $\Phi$ states that \changed{$``0"$ concatenated with $x$ is the same as $x$ with $``0"$, the numeric value of the string $x$ is equivalent to that of $y$, $y$ is longer than $x$,  $y$ is longer than $1000$ characters, and $x$ is longer than 1.  Notice that $\Phi$ is satisfiable. E.g., it has a model $x=``00"$ and $y=``0^{1002}"$}.
\changed{Although this toy example is seemingly trivial, all the state-of-the-art string constraint solvers we tried (including Z3, CVC4, and Z3Str3) cannot solve it within 10 minutes. }
